% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.6in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
%\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\setlist{nolistsep}
\setlength{\parskip}{2pt}
\setlength{\parindent}{0pt}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
%\lhead{(ii) CV}
%\rhead{Jake L. Weissman}
\lfoot{CV}
\rfoot{Page \thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\begin{document} 
 \small
\name{Jackie Lee ``JL'' Weissman\\[12pt]} % the \\[12pt] adds a blank line after name
 
 

\address{{\bf pronouns:} they/them/theirs {\emph{or}} she/her/hers\\ {\bf email:} jw4336@terpmail.umd.edu}
\address{{\bf website:} https://microbialgamut.com/}%{\bf twitter:} @jlw\_ecoevo}

 
\begin{resume} 
 
%\section{Objective} 
%Position as an undergraduate researcher at the Eco-Informatics Summer Institute

 \section{\underline{Positions:}} %\vspace{2mm}
\begin{itemize}[leftmargin=*]
\setlength\itemsep{0.5em}
\item[] {\bf Assistant Professor}, Department of Ecology \& Evolution and the Institute for Advanced Computational Science (IACS), Stony Brook University, Fall 2024 - Present
\item[] {\bf Director of Proposal Development}, City College of New York, New York, NY, 2023 - 2024
\begin{itemize}[leftmargin=*]
\item \emph{Previously: Assistant Director of Proposal Development}
\end{itemize}
%\item[] {\bf Assistant Director of Proposal Development}, CCNY, New York, NY, Summer/Fall 2023
\item[] {\bf Assistant Professor of Computational Biology}, Schmid College of Science and Technology, Chapman University, Orange, CA, Spring 2023 \emph{(tenure track, resigned for family reasons)}
\item[] {\bf Postdoctoral Fellow}, Department of Marine and Environmental Biology, University of Southern California, Los Angeles, CA, 2020 - 2022

 \section{Adjunct Appointments:}
\begin{itemize}[leftmargin=*]
\setlength\itemsep{0.5em}
\item[] {\bf Adjunct Assistant Professor of Biology}, the City College of New York, 2023 - Present
\item[] {\bf Adjunct Assistant Professor of Biological Sciences}, USC, 2023 - Present
\item[] {\bf Adjunct Instructor of Natural Sciences}, School of Art, The Cooper Union, 2023-2024
\end{itemize}

\section{\underline{Education}} %\vspace{2mm}

\begin{itemize}[leftmargin=*]
\setlength\itemsep{0.5em}
\item[] {\bf Ph.D., Behavior, Ecology, Evolution, and Systematics} (BEES; Fall 2019),
University of Maryland College Park, College Park, MD

\item[] {\bf Graduate Certificate, Computation and Mathematics for Biological Networks} (COMBINE; Fall 2019),
University of Maryland College Park, College Park, MD

\item[]  {\bf B.A., Mathematics and Biology}  (Spring 2015), Bard College, Annandale-on-Hudson, NY
\end{itemize}

 
 \end{itemize}
 
\section{\underline{External Funding}} %\vspace{2mm}
\begin{itemize} 
\item[] {\bf Chemical Currencies of a Microbial Planet (C-CoMP) Faculty Fellow} ($\$40,000$),\\ C-CoMP NSF STC, 2024\\\emph{Inferring Microbial Growth in Communities to Understand a Changing Climate}\\
\item[] {\bf NORDP Minority Serving Institution (MSI) Consultants Program (PI)}\\ ($\$150,000$, plus 600 hrs research development consulting, $\$20,000$ stipend, travel fund),\\ National Organization of Research Development Professionals, 2023\\\emph{The City College of New York (CCNY) Aims for R1 (CAR1)}\\
\item[] {\bf DoEd Research and Development Infrastructure Program (Key Personnel)}\\ \emph{(Coordinated proposal and wrote significant sections)} ($\$5$ million),\\ Department of Education, 2023\\\emph{Translational Research Excellence Across Disciplines (TREAD)}\\
\item[] {\bf NSF BRC-BIO (PI)} \emph{(awarded, declined when left Chapman position)} ($\$442,368$),\\ National Science Foundation, 2023\\\emph{Genomic and Metagenomic Maximum Growth Rate Estimation to Understand and Predict the Trajectories of Warming Permafrost Communities}\\
\item[] {\bf Simons Foundation Postdoctoral Fellowship in Marine Microbial Ecology} ($\$246,100$),\\ Simons Foundation, 2020-2023\\\emph{Drafting an Atlas of Prokaryotic Immune Strategy in the Global Oceans}
\end{itemize} 

\newpage
 
 \section{\underline{Publications} ($^\star$corresponding)} \vspace{2mm}
 
 
 \section{Preprints:} \vspace{0mm}
  
 \begin{enumerate}[leftmargin=*]
 \setlength\itemsep{0.25em}
 
\item Xu L., E. Zakem, \underline{J.L. Weissman$^\star$}. {\bf Improved maximum growth rate prediction from microbial genomes by integrating phylogenetic information.}. \emph{bioRxiv}
 
\item Laperriere S. M., B. Minch, \underline{J.L. Weissman}, S. Hou, Y.C. Yeh, J.C.L. Ignacio-Espinoza, N.A. Ahlgren, M. Moniruzzaman, J.A. Fuhrman. {\bf Phylogenetic proximity drives temporal succession of marine giant viruses in a five-year metagenomic time-series.} \emph{bioRxiv}

\item \underline{Weissman$^\star$ J.L.}, C.R. Chappell, B.F.R. de Oliveira, N. Evans, A.C. Fagre, D. Forsythe, S.A. Frese, R. Gregor, S.L. Ishaq, J. Johnston, S.B. Matsuda. {\bf Running a queer-and trans-inclusive faculty hiring process}. \emph{EcoEvoRxiv}

\item Zakem E.J., J. McNichol$^\dagger$, \underline{J.L. Weissman}$^\dagger$, Y. Raut, L. Xu, E.R. Halewood, C.A. Carlson, S. Dutkiewicz, J.A. Fuhrman, N.M. Levine. {\bf Predictable functional biogeography of marine microbial heterotrophs}. \emph{bioRxiv}

\item Buchanan P.J., X. Sun, \underline{J.L. Weissman}, E. Zakem. {\bf Oxygen intrusions sustain aerobic nitrite 
oxidation in anoxic marine zones}. \emph{bioRxiv}

\item \underline{Weissman$^\star$ J.L.}, E.R.O. Dimbo, A.I. Krinos, C. Neely, Y. Yag\"{ues}, D. Nolin, S. Hou, S. Laperriere, D.A. Caron, B. Tully, H. Alexander, J.A. Fuhrman. {\bf Estimating the maximal growth rates of eukaryotic microbes from cultures and metagenomes via codon usage patterns}. \emph{bioRxiv}

\item Ignacio-Espinoza J.C., S. Laperriere, Y. Yeh, \underline{J.L. Weissman}, S. Hou, M. Long, J.A. Fuhrman. {\bf Ribosome-linked mRNA-rRNA chimeras reveal active novel virus host associations}. \emph{bioRxiv}
 

  \end{enumerate} 

  
 \section{Peer Reviewed:} \vspace{0mm}
 
\begin{enumerate}[leftmargin=*]
 \setlength\itemsep{0.25em}
 
 \item Merchant S., \underline{J.L. Weissman}, E. MacLachlan. 2024. {\bf Creating a Broader Impacts Culture}. \emph{in press, Journal of Community Engagement and Scholarship}
 
 \item Xiao W., \underline{J.L. Weissman}, P.L.F. Johnson. 2024. {\bf Ecological drivers of CRISPR immune systems}. \emph{in press, mSystems}
 
 \item Connors E., A. Dutta, R. Trinh, N. Erazo, S. Dasarathy, H. Ducklow, \underline{J.L. Weissman}, Y.C. Yeh, O. Schofield, D. Steinberg, J. Fuhrman, J.S. Bowman. 2024. {\bf Microbial community composition predicts bacterial production across ocean ecosystems}. \emph{The ISME Journal}, p.wrae158.

 \item McDonald M.D., C. Owusu-Ansah, J.B. Ellenbogen, Z.D. Malone, M.P. Ricketts, S. Frolking, J.G. Ernakovich, M. Ibba, S.C. Bagby, \underline{J.L. Weissman$^\star$}. 2024. {\bf What is Microbial Dormancy?}. \emph{Trends in Microbiology}

 \item Gregor R., J. Johnston, L. Shu Yang Coe, T. Evans, D. Forsythe, R. Jones, D. Muratore, B.F. Rodrigues de Oliveira, R. Szabo, Y. Wan, J. Williams, Queer and Trans in Microbiology Consortium, \underline{J.L. Weissman$^\star$}. 2023. {\bf Building a Queer- and Trans-Inclusive Microbiology Conference}. \emph{mSystems} 8(5), e00433-23.
 
\item Fletcher-Hoppe C., Y.C. Yeh, Y. Raut, \underline{J.L. Weissman}, J.A. Fuhrman. 2023. {\bf Symbiotic diazotrophic UCYN-A strains co-occurred with El Niño, relaxed upwelling, and varied eukaryotes over 10 years off Southern California Bight}. \emph{ISME Communications} 3(1), 63
 
  \item \underline{Weissman$^\star$ J.L.}, M. Peras, T.P. Barnum, J.A. Fuhrman. 2022. {\bf Benchmarking community-wide estimates of growth potential from metagenomes using codon usage statistics}. \emph{mSystems} 7(5), e00745-22.
  
    \item  Tao J., W. Wang, \underline{J.L. Weissman}, Y. Zhang , S. Chen, Y. Zhu, C. Zhang, and S. Hou. 2022. {\bf Size-fractionated microbiome observed during an eight-month long sampling in Jiaozhou Bay and the Yellow Sea}. \emph{Scientific Data} 9(1), 1-8.
 
 \item Gleich S.J, J.A. Cram, \underline{J.L. Weissman}, D.A. Caron. 2022. {\bf NetGAM: Using generalized additive models to improve the predictive power of ecological network analyses constructed using time-series data}. \emph{ISME Communications} 2(1), 23
 
\item \underline{Weissman$^\star$ J.L.}, S. Hou, J.A. Fuhrman. 2021. {\bf Estimating maximal microbial growth rates from cultures, metagenomes, and single cells via codon usage patterns}. \emph{Proceedings of the National Academy of Sciences} 118(12), e2016810118. 
 
\item \underline{Weissman$^\star$ J.L.}, E.O. Alseth, S. Meaden, E.R. Westra, J.A. Fuhrman. 2021. {\bf Immune Lag Is a Major Cost of Prokaryotic Adaptive Immunity During Viral Outbreaks}. \emph{Proceedings of the Royal Society B} 288, 20211555.

\item \underline{Weissman J.L.}, ..., P.L.F. Johnson, D. Karig, W.F. Fagan, S. Bewick. 2021. {\bf Exploring the functional composition of the human microbiome using a hand-curated microbial trait database.} \emph{BMC Bioinformatics} 22(1), 1471-2105.

\item Tully B.J, J. Buongiorno, ..., L.E. Valentin-Alvarado, \underline{J.L. Weissman}, BVCN Instructor Consortium. 2021. {\bf The Bioinformatics Virtual Coordination Network: an open-source and interactive learning environment.} \emph{Frontiers in Education} 6, 394.

\item \underline{Weissman J.L.}, A. Stoltzfus, E.R. Westra, P.L.F. Johnson. 2020. {\bf Avoidance of Self During CRISPR Immunization.} \emph{Trends in Microbiology} 28(7), 543-553.

\item \underline{Weissman J.L.} \& P.L.F. Johnson. 2020. {\bf Network-Based Prediction of Novel CRISPR-Associated Genes in Metagenomes.} \emph{mSystems} 5(1), e00752-19.

\item Mart\'{i}-Carreras J., ..., \underline{J.L. Weissman}, V. Zalunin, A. Efremov, B. Busby. 2020. {\bf NCBI’s Virus Discovery Codeathon: Building the “FIVE” -- Federated Index of Viral Experiments API index.} \emph{Viruses} 12(12), 1424.
 
 \item \underline{Weissman J.L.}, W.F. Fagan, P.L.F. Johnson. 2019. {\bf Linking high GC content to the repair of double strand breaks in prokaryotic genomes.} \emph{PLOS Genetics} 15(11), e1008493.\\ %(https://doi.org/10.1371/journal.pgen.1008493).
 
 \item \underline{Weissman J.L.}, R. Laljani, W.F. Fagan, P.L.F. Johnson. 2019. {\bf Visualization and prediction of CRISPR incidence in microbial trait-space to identify drivers of antiviral immune strategy}. \emph{The ISME Journal} 13(10), 2589-2602. %(https://doi.org/10.1038/s41396-019-0411-2)
 
 \item Bewick S., E. Gurarie, \underline{J.L. Weissman}, J. Beattie, C. Davati, R. Flint, P. Thielen, F. Breitwieser, D. Karig, W.F. Fagan. 2019. {\bf Trait-Based Analysis of the Human Skin Microbiome}. \emph{Microbiome} 7(1), 101.  %(https://doi.org/10.1186/s40168-019-0698-2)

 \item \underline{Weissman J.L.}, W.F. Fagan, P.L.F. Johnson. 2018. {\bf Selective maintenance of multiple CRISPR arrays across prokaryotes}. \emph{The CRISPR Journal} 1(6), 405-413. %(https://doi.org/10.1089/crispr.2018.0034) 
 
\item \underline{Weissman J.L.}, R. Holmes, R. Barrangou, S. Moineau, W.F. Fagan, B. Levin, P.L.F. Johnson. 2018. {\bf Immune Loss as a Driver of Coexistence During Host-Phage Coevolution}. \emph{The ISME Journal} 12(2), 585-597. %(https://doi.org/10.1038/ismej.2017.194)

\end{enumerate} 

 
\section{Outreach Publications:} \vspace{0mm}

 \begin{enumerate}[leftmargin=*]

\item \underline{Weissman J. L.}, S. Hou, J.A. Fuhrman. 2022. {\bf Using DNA to Predict How Fast Bacteria Can Grow}. \emph{Frontiers Young Minds.}

\item \underline{Weissman J. L.}, H.H. Yiu, P.L.F. Johnson. 2019. {\bf What Bacteria Do When They Get Sick}. \emph{Frontiers Young Minds.}

  \end{enumerate} 


\section{\underline{Teaching}} \vspace{2mm}

{\bf Teaching at City College (Proposal Development),} 
\begin{itemize} \itemsep -2pt
\item Designed and taught {\bf Early Career Faculty Writing Club} (F23-S24)
\item Designed and taught {\bf Broader Impacts Writing Workshop} (January 2024)
\item Designed and taught {\bf Writing an Effective DOE Promoting Inclusive and Equitable Research (PIER) Plan Workshop} (October 24)
\end{itemize}


{\bf Teaching at The Cooper Union,} 
\begin{itemize} \itemsep -2pt
\item Designed \& taught interdisciplinary non-major course {\bf RS-201-I: Genomes \& Society} examining the science and the social implications of genomics (F23, S24)
\end{itemize}

{\bf Teaching at Chapman University,} 
\begin{itemize} \itemsep -2pt
\item Redesigned \& Taught {\bf BIOL317: General Microbiology} (S23)
\item Designed interdisciplinary upper-level elective {\bf BIOL460: Genomes \& Society} examining both the science and the social, ethical, and historical context of human genomics research
\end{itemize}

{\bf Instructor,} Qlife Quantitative Biology Winter School: Quantitative Viral Dynamics Across Scales, D\'{e}partement de Biologie, \'{E}cole normale sup\'{e}rieure, Paris, France, March 2022

{\bf Facilitator,} {Microbial Ecology Reading Group}, SBU, 2024-

{\bf Facilitator,} {Marine and Environmental Biology Statistics Reading Group}, USC, 2020-2022

{\bf Instructor,} Bioinformatics Virtual Coordination Network, 2020-2021\\
\verb|https://biovcnet.github.io/|

{\bf Guest Lecturer} \\
\emph{Stony Brook University}
\begin{itemize} \itemsep -2pt
\item BEE556: Research Areas in Ecology \& Evolution, Fall 2024
\item GRD500: Responsible Conduct of Research, Fall 2024
\end{itemize}
\emph{Reed College}
\begin{itemize} \itemsep -2pt
\item BIO331: Computational Systems Biology, Fall 2024
\end{itemize}
\emph{University of Maryland College Park}
\begin{itemize} \itemsep -2pt
\item BIOL709F: Statistics and Modeling for Biologists, Spring 2018
\item BSCI464: Microbial Ecology, Spring 2018 
\item BSCI405: Population and Evolutionary Genetics, Spring 2017
\end{itemize}

{\bf Teaching Assistant, Calculus for the Life Sciences,} Department of Biology, University of Maryland College Park, Fall 2015%\\$\;$ \hfill  Fall 2015

{\bf Teaching Assistant, Bridge to Enter Advanced Mathematics (BEAM)}, The Art of Problem Solving Foundation, Cambridge, MA, Summer 2012 and 2015 %\\$\;$ \hfill  

{\bf Project Head, Bard Math Circle}, Bard College, Annandale-on-Hudason, NY, 2011-2015
%\item Assisted in teaching problem-solving and special-topics classes (e.g. number theory, proofs, graph theory) at an advanced summer mathematics program for underserved middle-school students
%\end{itemize}

\section{\underline{Mentoring}} \vspace{2mm}
{\bf Mentorship Training}, \emph{CIMER Training}, Stony Brook University, 2024\\
{\bf Scientific ``Thought-Partner''}, \emph{Artist in Residency Program}, GenSpace, 2024\\
{\bf Faculty Adviser,} \emph{oSTEM at Chapman}, Chapman University, 2023\\
{\bf Panelist,} \emph{Path of Professorship Workshop}, MIT, 2022, 2023, 2024\\
{\bf Panelist,} \emph{Effective Time Management for New Graduate Students (Orientation)}, USC, 2022\\
{\bf Workshop Organizer,} \emph{Mentoring Undergraduate Researchers: A Practical Guide for Graduate Student Mentors}, University of Maryland College Park, 2019\\
{\bf Undergraduate Researchers Mentored \emph{\footnotesize{($^{\star}$coauthor, $^{\dagger}$presented at symposium or conference)}}} \\
\emph{Stony Brook University:}
\begin{itemize}[leftmargin=*]
\item[] Jesse Natarajan (Fall 2024 - Spring 2025; Senior Thesis)
\end{itemize}
\emph{Chapman University:}
\begin{itemize}[leftmargin=*]
\item[] Athenna Gonzalez (Spring 2023)
\end{itemize}
\emph{University of Southern California:}
\begin{itemize}[leftmargin=*]
\item[] Edward-Robert Dimbo$^{\star}$ (Winter 2021 - Summer 2022; GGURE)
\item[] James Rosas$^{\dagger}$ (Summer 2021; National Summer Undergraduate Research Project, nsurp.org)
\item[] Yuniba Yag{\"u}es$^{\star\dagger}$ (Summer 2020; National Summer Undergraduate Research Project, nsurp.org)
\item[] Oscar Escobedo$^{\dagger}$ (Summer 2020; National Summer Undergraduate Research Project, nsurp.org)
\end{itemize}
\vspace{1mm}
\emph{University of Maryland College Park:}
\begin{itemize}[leftmargin=*]
\item[] Rohan Laljani$^{\star\dagger}$ (Fall 2017 - Summer 2019)
\item[] Vinay Veluvolu$^{\dagger}$ (Summer 2018 - Summer 2019)
\item[] Julia Gall$^{\dagger}$ (Fall 2018 - Spring 2019; College Park Scholars)
\item[] Cori Butkiewicz (Summer 2017 - Spring 2018)
\item[] Nicholas Penn (Spring 2017 - Summer 2017)
\end{itemize}


\section{\underline{Service}} \vspace{2mm}

{\bf Judge,} CUNY Summer Research Program Poster Session, 2024

{\bf Conference Chair,} NYC Future Energy Conference, CCNY, 2024

{\bf Search Committee,} Grant Writer, CCNY, 2024

{\bf Search Committee,} Associate Provost for Research, CCNY, 2024

{\bf Panelist,} Pride in Microbiology Network, 2023

{\bf Member,} Committee on Inclusive Excellence, National Organization of Research Development Professionals, NORDP, 2023-

{\bf Co-Founder,} Working Group on Trans- and Queer-Inclusive Conferences in Microbiology, 2022-2023

{\bf Organizer,} {Inclusive Teaching Workshop}, Chapman University, 2023

{\bf DEI Taskforce Member,} {Schmid College}, Chapman University, 2022-2023

{\bf Facilitator,} DEI Journal Club on Ableism in Evolutionary Biology , USC, 2022

{\bf Reviewer,} CAREER Awards, NSF, 2022

{\bf Session Co-Chair,} {Ocean Sciences Meeting}, 2022

{\bf DEI Committee Member,} {Dept. of Marine and Environmental Biology (MEB)}, USC, 2021-2022

{\bf DEI Subcommittee on Reporting Member,} {MEB}, USC, 2021-2022

{\bf Judge,} ASM Early Career Flash Talks, October 2021

{\bf Conference Organizing Committee,} {Holistic Bioinformatics Approaches Used in Microbiome Research}, Bioinformatics Virtual Coordination Network, Summer 2020-Summer 2021

{\bf Facilitator,} {Pride Month Workshop on Queering Professionalism}, USC, June 2021

{\bf Co-Organizer,} {Pride Month Programming for MEB}, USC, June 2021

%{\bf Participant,} {Unlearning Racism in Geoscience (URGE)}, USC, Spring 2021

{\bf Poster Judge,} {CRISPR 2021 Meeting}, June 2021

{\bf Secretary-Treasurer,} {BEES Student Taskforce (BEESst)}, UMD-CP, Fall 2018-Spring 2019 %\\$\;$ \hfill  Fall 2018-Spring 2019

{\bf Co-President,} {BEES Student Taskforce (BEESst)}, UMD-CP, Fall 2017-Spring 2018

{\bf Graduate Mentor,} {Biological Sciences Graduate Program}, UMD-CP, Fall 2016, 2017 %\\$\;$ \hfill  Fall 2016, 2017

{\bf Journal Reviewer:} ISME J, PNAS, Current Biology, Nature Communications, mSystems, Microbiome, Proceedings B, PLoS Comp Bio, Marine Genomics, npj Biofilms and Microbiomes, BMC Bioinformatics, J Theor Biol

\section{\underline{Community Engagement}}\vspace{2mm}
{\bf Collaborator/Bioinformatics Facilitator}, Microbial Reef Project, GenSpace, 2024-\\
{\bf Participant,} SciArt Workshop, BraiNY \& Genspace, 2023\\
{\bf Co-Founder,} Postdoc Outreach Project with LA Public Library, USC, 2020-2022\\
{\bf Project Mentor,} Terps in Space, 2017, 2018, 2022\\
{\bf Tutor \& Mentor,} Joint Educational Project, USC, Spring 2020\\
{\bf Lead Organizer,} Frontiers Young Minds Writing Group, USC, Winter-Spring 2020\\
{\bf Panel Reviewer,} Student Spaceflight Experiments Program (SSEP) 2016-2019\\
{\bf Maryland Day Organizer,} Biological Sciences, UMD-CP, 2016-2018\\
{\bf Project Leader,} Bard Math Circle, Annandale-on-Hudson, NY, 2013-2015 \\
{\bf Public Talk,} GradTerps Exchange, University of Maryland, Spring 2019\\
{\bf Public Talk,} Skype a Scientist, Summer 2020

  
   \section{\underline{Other Fellowships and Awards}} %\vspace{2mm}
\begin{itemize}[leftmargin=*]
%\item[] Simons Postdoctoral Fellowship in Marine Microbial Ecology (Simons Foundation, 2019)
%\item[] Biology Travel Award (UMD-CP, 2019 and 2016)
\item[] COMBINE Network Science Fellowship ($\$35,859$, UMD/NSF DGE-1632976, 2018)
\item[] Devra Kleiman Memorial Scholarship ($\$2,500$, UMD, 2018)
\item[] GAANN Mathematical Biology Fellowship ($\$74,598$, UMD/U.S. Department of Education, 2015)
\item[] The Flagship Fellowship ($\$50,000$, UMD, 2015)
\item[] The Dean's Fellowship ($\$10,000$, UMD, 2015)
\item[] The Harry J. Carman Scholarship (Bard College, 2014)
\item[] The John Bard Scholarship (Division of Science, Math and Computing, Bard College, 2013)
\item[] George I. Alden Scholar (George I. Alden Trust, 2012)%for the 2012-2013 academic year 
\item[] The Excellence and Equal Cost Scholarship (Bard College, 2011) 
\item[] The Bishop Scholarship (The Bishop Scholarship Foundation, 2011)
\end{itemize}
  
\section{\underline{Summer Schools:}}%\vspace{2mm}
\begin{itemize}[leftmargin=*]
%\item[] {\bf Virus Hunting in the Cloud Codeathon}, NCBI/UMIACS, College Park, MD, 2019
\item[] {EMergent Ecosystem Responses to ChanGE Summer Program}, EMERGE, NH, 2022
\item[] {Microbial Diversity Course}, Marine Biological Laboratory, Woods Hole, MA, 2018
\item[] {The Search for Selection}, NIMBioS, Knoxville, TN, 2018
\item[] {Complex Systems Summer School}, Santa Fe Institute, Santa Fe, NM, 2017
\item[] {Quantitative Laws II}, Lake Como School of Advanced Studies, Italy, 2016  
%\item[] {\bf Quantitative Laws II Workshop}, Lake Como School of Advanced Studies, Italy, 2016  
 \end{itemize}  
 
 \newpage
  
   \section{\underline{Invited Talks}} \vspace{2mm}
    \begin{enumerate}[leftmargin=*]
\item Microbiomes and Social Equity Seminar Series, 2024 (upcoming)
\item Invited Abstract, American Geosciences Union, 2024 (upcoming)
\item Department of Natural Resources, University of New Hampshire, NY, 2024
\item Department of Biology, Hofstra University, NY, 2024, 2024
\item ECR Viromics Seminar, Ohio State University/European Virus Bioinformatics Center, 2024
\item Department of Ecology and Evolution, Stony Brook University, 2024
\item Institute for Advanced Computational Science (IACS), Stony Brook University, 2024
\item Track Hub, American Society for Microbiology, TX, 2023 (Declined)
\item Physics of Life Sciences, Massachusetts Institute of Technology, MA, 2022
\item Department of Biology, California State University Los Angeles, CA, 2022
\item Department of Biology, University of Minnesota Duluth, MN, 2022
\item Simons Collab. on Comp. Biogeochem. Modeling of Marine Ecosystems (CBIOMES), 2021
\item Center for Dark Energy Biosphere Investigations (C-DEBI), 2021
\item Department of Biology, University of Pittsburgh, PA, 2021
\item Center for Advanced Biotechnology and Medicine, Rutgers University, NJ, 2021
\item Department of Biology, Chapman University, CA, 2021
\item Department of Biology, Westchester University, PA, 2021
\item Department of Biology, Lake Forest College, IL, 2021
\item Department of Biology, San Diego State University, CA, 2021
\item Computation and Mathematics for Biological Networks (COMBINE), UMD, MD, 2020
\item Department of Marine and Environmental Biology, USC, CA, 2020
\item Environment and Sustainability Institute, University of Exeter, Penryn, UK, 2019
\item Clemson University, Clemson, SC, Dec 2018
\end{enumerate}

 \section{\underline{Conference Presentations} \emph{{($^{\star}$poster, $^{\dagger}$talk)}}} \vspace{2mm}
 
 {\bf Demonstrating commitment with limited resources}
 \begin{itemize}
 \item National Organization of Research Development Professionals Conference, May 2024$^{\dagger}$
 \end{itemize} 
 
 {\bf Building a Community of Practice and Engagement (COPE) - A CUNY Broader Impacts Framework}
 \begin{itemize}
 \item Advancing Research Impacts in Society (ARIS) Summit, April 2024$^{\star}$
 \end{itemize}
 
 {\bf Predicting maximal microbial growth rates from genomes and metagenomes for prokaryotes and eukaryotes}
 \begin{itemize}
 \item Marine Microbes, Gordon Research Conference and Seminar, Switzerland, May 2022$^{\dagger\star}$
 \item Fifth Workshop On Trait-Based Approaches to Ocean Life, Knoxville, TN, January 2022$^{\star}$
 \item Microbial Ecology \& Evolution Virtual (MEEVirtual), online, August 2020$^{\star}$
 \item CBIOMES Annual Meeting, online, June 2020$^{\star}$
 \end{itemize}
 
{\bf Linking selection for high GC content to repair of double strand breaks in prokaryotic genomes}
 \begin{itemize}
 \item Microbial Population Biology, Gordon Research Conference and Seminar, NH, July 2019$^{\star}$
 \end{itemize} 
 
{\bf Ecology Shapes Microbial Immune Strategy: Temperature and Oxygen as Determinants of the Incidence of CRISPR Adaptive Immunity} 
 \begin{itemize}
 \item CRISPR Ecology and Evolution, the Royal Society, London, UK, February 2019$^{\star}$
 \item Microbial Eco-Evolutionary Dynamics, Instituto Gulbenkian De Ci\^{e}ncia, Oeiras, Portugal, October 2018$^{\star}$
 \end{itemize}
 
 {\bf Is Having more than one CRISPR array adaptive?}
 \begin{itemize}
 \item Microbial Population Biology, Gordon Research Conference and Seminar, NH, July 2017$^{\star}$
 \end{itemize}
 
  {\bf Immune Loss as a Driver of Coexistence During Host-Phage Coevolution}
 \begin{itemize}
 \item Evolution in Philadelphia Conference (EPiC), UPenn, April 2017$^{\dagger}$
 \item Molecular Coevolution Workshop, Princeton Center for Theoretical Science, April 2016$^{\star}$
 \end{itemize}


\end{resume} 
\end{document} 

