% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.6in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
%\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\setlist{nolistsep}
\setlength{\parskip}{2pt}
\setlength{\parindent}{0pt}
\usepackage{hyperref}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
%\lhead{(ii) CV}
%\rhead{Jake L. Weissman}
\lfoot{CV}
\rfoot{Page \thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\begin{document} 
 \small
\name{Jackie Lee ``JL'' Weissman\\[12pt]} % the \\[12pt] adds a blank line after name
 
 

\address{{\bf pronouns:} they/them/theirs {\emph{or}} she/her/hers\\ {\bf email:} jackie.weissman@stonybrook.edu}
\address{{\bf website:} https://microbialgamut.com/}%{\bf twitter:} @jlw\_ecoevo}

 
\begin{resume} 
 

 \section{\underline{Publications Since Joining E\&E} ($^\star$corresponding)} \vspace{1mm}
 

\begin{enumerate}[leftmargin=*]
 \setlength\itemsep{0.2em}
 
 \item Laperriere S. M., B. Minch,  \underline{J.L. Weissman}, S. Hou, Y.C. Yeh, J.C.L. Ignacio-Espinoza, N.A. Ahlgren, M. Moniruzzaman, J.A. Fuhrman. 2025. {\bf Phylogenetic proximity is a key driver of temporal succession of marine giant viruses in a five-year metagenomic time-series.} \emph{ISME Communications} ycaf217
 
 \begin{itemize}
 	\item Role: I consulted closely with lead author on statistical analysis of time series in figures 1-3 (including writing code) and conceptualized the analysis in and wrote the code to generate figures 4 and 5. Assisted with initial drafting of analysis and subsequent manuscript review. 
 \end{itemize}
 
\item Osburn E.D., \underline{J.L. Weissman}, M.S. Strickland, M. Bahram, B.W. Stone, S.G. McBride. 2025. {\bf Relative abundances of bacterial phyla are strong indicators of community-scale microbial growth rates in soil}. \emph{Environmental Microbiome} 20(131)

 \begin{itemize}
 	\item Role: I consulted with lead author on methods for metagenomic growth inference and proposed the analysis in figure 3. Assisted in writing by reviewing manuscript drafts.
 \end{itemize}
 
\item Kong S., ... C.K. Lardner, \underline{J.L. Weissman$^\star$}. 2025. {\bf Metagenomes and Metagenome-Assembled Genomes from Tidal Lagoons at a New York City Waterfront Park}. \emph{PeerJ} 13:e20081

 \begin{itemize}
 	\item Role: Senior author. Supervised team consisting of community biologists at Genspace, including guiding proposal writing to fund the project, advising on sampling protocols and assisting with sampling in the field, running bioinformatics workshops, and drafting the first draft of the manuscript and coordinating the review process.
 \end{itemize}
 
\item Sinnott-Armstrong N., D. Forsythe, J.M. Benoit, C.R. Chappell, L.S.Y. Coe, B.F.R. de Oliveira, N.C. Evans, A.C. Fagre, J.M. Gilligan, M. Hamilton, C.M. Henneberry, S.L. Ishaq, J. Johnston, E. Krichilsky, J. Alcira Lopez, K. McMonigal, M. Ortiz Alvarez de la Campa, R. Rahman, N.E. Schwartz, L. Talluto, E.J. Taylor, J.M. Vargas-Muñiz, \underline{J.L. Weissman}. 2025. {\bf Protect Transgender Scientists}. \emph{Science}  388(6753), 1283-1284.

 \begin{itemize}
 	\item Role: I am the lead facilitator and co-founder of AQTES, which published this letter. I took a step back during the writing process to let other team members have a chance to lead a project, but I initiated the writing process for this piece, developed the AQTES guidelines we follow to write all of our projects, and worked over years to build this team. I provided detailed feedback on drafts throughout the writing process.
  \end{itemize}
 
\item Buchanan P.J., X. Sun, \underline{J.L. Weissman}, D. McCoy, D. Bianchi, E. Zakem. 2025. {\bf Oxygen intrusions sustain aerobic nitrite 
oxidation in anoxic marine zones}. \emph{Science} 388(6751), 1069-1074.
 
 \begin{itemize}
 	\item Role: I contributed the analysis in figure 5, including by developing a custom predictive model in a bioinformatics software my lab group develops (gRodon) to improve performance on the microbial groups focused on in this study. I also implemented this custom model in our publicly available R package for others in this field to use. 
  \end{itemize}
 
\item Zakem E.J., J. McNichol$^\dagger$, \underline{J.L. Weissman}$^\dagger$, Y. Raut, L. Xu, E.R. Halewood, C.A. Carlson, S. Dutkiewicz, J.A. Fuhrman, N.M. Levine. 2025. {\bf Functional biogeography of marine microbial heterotrophs}. \emph{Science} 388(6749), eado5323.

 \begin{itemize}
 	\item Role: I am co-second author on this paper, which was a close collaborative effort between the first three listed authors: Zakem handling biogeochemical modeling, McNichol processing sequencing data and curating taxonomic annotation, and myself developing the genomic index of copiotrophy that allowed us to link modeled microbial functional classes to environmental sequencing data. I was primarily responsible for the data and analysis shown in figure 4. 
 \end{itemize}
 
\item Xu L., E. Zakem, \underline{J.L. Weissman$^\star$}. 2025. {\bf Improved maximum growth rate prediction from microbial genomes by integrating phylogenetic information.} \emph{Nature Communications} 16(1), 1-10.

\begin{itemize}
	\item Role: Senior author. I supervised the lead author (a colleague's postdoc) on this project, including proposing the original idea for phylogenetically refined genomic growth rate prediction and through weekly 1:1 meetings where we discussed project progress and challenges. Along with the lead author, we drafted the original manuscript draft togehter.
\end{itemize}

\item Gleich S., L. Mesrop, J. Cram, \underline{J.L. Weissman}, S. Hu, Y. Yeh, J. Fuhrman, D. Caron. 2025. {\bf With a little help from my friends: Importance of protist-protist interactions in structuring marine protistan communities in the San Pedro Channel}. \emph{mSystems} e01045-24.

\begin{itemize}
	\item Role: Served as co-mentor of lead author when I was a postdoc and they were a graduate student, including meeting with them weekly to guild the statistical methods development that enabled this work (see Gliech et al. 2022 below). Provided detailed feedback on manuscript drafts.
\end{itemize}
 
\item \underline{Weissman$^\star$ J.L.}, C.R. Chappell, B.F.R. de Oliveira, N. Evans, A.C. Fagre, D. Forsythe, S.A. Frese, R. Gregor, S.L. Ishaq, J. Johnston, Bittu K.R., S.B. Matsuda, S. McCarren, M.O.A. de la Campa, T.A. Roepke, N. Sinnott-Armstrong, C.S. Stobie, L. Talluto, J. Vargas-Muñiz, The Advancing Queer and Trans Equity in Science (AQTES) Consortium. 2024. {\bf Queer- and trans-inclusive faculty hiring—A call for change}. \emph{PLOS Biology} 22(11), e3002919.

\begin{itemize}
	\item Role: Lead author. I wrote the initial manuscript draft, assembled a team of over 50 scientists from 12 countries and 5 continents, and coordinated multiple public review periods for our proposed guidance. 
\end{itemize}
 
 \item Merchant S., \underline{J.L. Weissman}, E. MacLachlan. 2024. {\bf Creating a Broader Impacts Culture}. \emph{Journal of Community Engagement and Scholarship} 17(2), 13.
 
 \begin{itemize}
 	\item Role: I collaborated closely with the lead author to develop these recommendations during my time as director of proposal development at CCNY, including by running several of the workshops and focus groups described in the study myself.
 \end{itemize}
 
 \item Xiao W., \underline{J.L. Weissman}, P.L.F. Johnson. 2024. {\bf Ecological drivers of CRISPR immune systems}. \emph{mSystems} e00568-24
 
 \begin{itemize}
 	\item Role: I served as a senior graduate student mentor to the lead author when we were both in our PhD program together, including by proposing some of the analyses in this paper. This work started in 2019, but I contributed feedback on the manuscript revision process up to its publication in 2024.
 \end{itemize}
 
 \end{enumerate} 
 
  \section{Preprints:} \vspace{0mm}
  
 \begin{enumerate}[leftmargin=*]
 \setlength\itemsep{0.25em}

\item \underline{Weissman J.L.$^\star$},  A. Walling, E. Zakem.{\bf  On Copiotrophy and Temperature: Controls on Microbial Maximum Growth Rate Versus Translation Rate Optimization.}  \emph{bioRXiv, under review ISME J} 

\begin{itemize}
 	\item Role: Lead author. I wrote the initial draft of this manuscript and developed the analyses it describes. This is a follow-up on my part of  the work described in Zakem et al. (above)
 \end{itemize}
 
\item Natarajan J. \& \underline{J.L. Weissman$^\star$}. {\bf Assembly-Free Short-Read Metagenomic Maximum Growth Rate Prediction.} \emph{bioRXiv, resubmitted after revision (enthusiastic reviewers)} 

\begin{itemize}
 	\item Role: Senior author. First author is a former SBU undergrad (CS major, Bio minor) and this manuscript was developed out of her honors thesis in my lab (2024-2025). I supervised all aspects of this project. 
 \end{itemize}
 
\item \underline{Weissman J.L.$^\star$}, J.M. O'Brien, N.D. Blais, H. Holland-Moritz, K. Shek, R.A. Barbato, T.A. Douglas, J. Gilman Ernakovich. {\bf Growth Optimization Predicts Microbial Success in a Permafrost Thaw Experiment.} \emph{bioRXiv, submitted to Siol Biology and Biochemistry}

\begin{itemize}
 	\item Role: Lead author. Using experiments from my collaborator's lab (Ernakovich) I developed a novel bioinformatic approach to analyze these data.
\end{itemize}

\item Reynolds, R., A.C. Weiss, C.C. James, C.Y. Kojima, \underline{J.L. Weissman}, J.C. Thrash, N.M. Levine. {\bf Emergent Metabolic Niches for Marine Heterotrophs}. \emph{bioRxiv, in revision Science Advances}

\begin{itemize}
 	\item Role: I provided genomic growth rate predictions tailored to the specific modeling applications described in this paper (contributed to Table 1, Figure S9, and Figure S11). I also reviewed manuscript drafts and provided detailed feedback.
\end{itemize}

\end{enumerate} 


 \section{\underline{Publications Prior to Joining E\&E} ($^\star$corresponding)} \vspace{1mm}
 

\begin{enumerate}[leftmargin=*]
 \setlength\itemsep{0.2em}
 
 
 
 \item Connors E., A. Dutta, R. Trinh, N. Erazo, S. Dasarathy, H. Ducklow, \underline{J.L. Weissman}, Y.C. Yeh, O. Schofield, D. Steinberg, J. Fuhrman, J.S. Bowman. 2024. {\bf Microbial community composition predicts bacterial production across ocean ecosystems}. \emph{The ISME Journal}, p.wrae158.


 \item McDonald M.D., C. Owusu-Ansah, J.B. Ellenbogen, Z.D. Malone, M.P. Ricketts, S. Frolking, J.G. Ernakovich, M. Ibba, S.C. Bagby, \underline{J.L. Weissman$^\star$}. 2024. {\bf What is Microbial Dormancy?}. \emph{Trends in Microbiology}

 \item Gregor R., J. Johnston, L. Shu Yang Coe, T. Evans, D. Forsythe, R. Jones, D. Muratore, B.F. Rodrigues de Oliveira, R. Szabo, Y. Wan, J. Williams, Queer and Trans in Microbiology Consortium, \underline{J.L. Weissman$^\star$}. 2023. {\bf Building a Queer- and Trans-Inclusive Microbiology Conference}. \emph{mSystems} 8(5), e00433-23.
 
\item Fletcher-Hoppe C., Y.C. Yeh, Y. Raut, \underline{J.L. Weissman}, J.A. Fuhrman. 2023. {\bf Symbiotic diazotrophic UCYN-A strains co-occurred with El Niño, relaxed upwelling, and varied eukaryotes over 10 years off Southern California Bight}. \emph{ISME Communications} 3(1), 63
 
  \item \underline{Weissman$^\star$ J.L.}, M. Peras, T.P. Barnum, J.A. Fuhrman. 2022. {\bf Benchmarking community-wide estimates of growth potential from metagenomes using codon usage statistics}. \emph{mSystems} 7(5), e00745-22.
  
    \item  Tao J., W. Wang, \underline{J.L. Weissman}, Y. Zhang , S. Chen, Y. Zhu, C. Zhang, and S. Hou. 2022. {\bf Size-fractionated microbiome observed during an eight-month long sampling in Jiaozhou Bay and the Yellow Sea}. \emph{Scientific Data} 9(1), 1-8.
 
 \item Gleich S.J, J.A. Cram, \underline{J.L. Weissman}, D.A. Caron. 2022. {\bf NetGAM: Using generalized additive models to improve the predictive power of ecological network analyses constructed using time-series data}. \emph{ISME Communications} 2(1), 23
 
\item \underline{Weissman$^\star$ J.L.}, S. Hou, J.A. Fuhrman. 2021. {\bf Estimating maximal microbial growth rates from cultures, metagenomes, and single cells via codon usage patterns}. \emph{Proceedings of the National Academy of Sciences} 118(12), e2016810118. 
 
\item \underline{Weissman$^\star$ J.L.}, E.O. Alseth, S. Meaden, E.R. Westra, J.A. Fuhrman. 2021. {\bf Immune Lag Is a Major Cost of Prokaryotic Adaptive Immunity During Viral Outbreaks}. \emph{Proceedings of the Royal Society B} 288, 20211555.

\item \underline{Weissman J.L.}, ..., P.L.F. Johnson, D. Karig, W.F. Fagan, S. Bewick. 2021. {\bf Exploring the functional composition of the human microbiome using a hand-curated microbial trait database.} \emph{BMC Bioinformatics} 22(1), 1471-2105.

\item Tully B.J, J. Buongiorno, ..., L.E. Valentin-Alvarado, \underline{J.L. Weissman}, BVCN Instructor Consortium. 2021. {\bf The Bioinformatics Virtual Coordination Network: an open-source and interactive learning environment.} \emph{Frontiers in Education} 6, 394.

\item \underline{Weissman J.L.}, A. Stoltzfus, E.R. Westra, P.L.F. Johnson. 2020. {\bf Avoidance of Self During CRISPR Immunization.} \emph{Trends in Microbiology} 28(7), 543-553.

\item \underline{Weissman J.L.} \& P.L.F. Johnson. 2020. {\bf Network-Based Prediction of Novel CRISPR-Associated Genes in Metagenomes.} \emph{mSystems} 5(1), e00752-19.

\item Mart\'{i}-Carreras J., ..., \underline{J.L. Weissman}, V. Zalunin, A. Efremov, B. Busby. 2020. {\bf NCBI’s Virus Discovery Codeathon: Building the “FIVE” -- Federated Index of Viral Experiments API index.} \emph{Viruses} 12(12), 1424.
 
 \item \underline{Weissman J.L.}, W.F. Fagan, P.L.F. Johnson. 2019. {\bf Linking high GC content to the repair of double strand breaks in prokaryotic genomes.} \emph{PLOS Genetics} 15(11), e1008493. %(https://doi.org/10.1371/journal.pgen.1008493).
 
 \item \underline{Weissman J.L.}, R. Laljani, W.F. Fagan, P.L.F. Johnson. 2019. {\bf Visualization and prediction of CRISPR incidence in microbial trait-space to identify drivers of antiviral immune strategy}. \emph{The ISME Journal} 13(10), 2589-2602. %(https://doi.org/10.1038/s41396-019-0411-2)
 
 \item Bewick S., E. Gurarie, \underline{J.L. Weissman}, J. Beattie, C. Davati, R. Flint, P. Thielen, F. Breitwieser, D. Karig, W.F. Fagan. 2019. {\bf Trait-Based Analysis of the Human Skin Microbiome}. \emph{Microbiome} 7(1), 101.  %(https://doi.org/10.1186/s40168-019-0698-2)

 \item \underline{Weissman J.L.}, W.F. Fagan, P.L.F. Johnson. 2018. {\bf Selective maintenance of multiple CRISPR arrays across prokaryotes}. \emph{The CRISPR Journal} 1(6), 405-413. %(https://doi.org/10.1089/crispr.2018.0034) 
 

\item \underline{Weissman J.L.}, R. Holmes, R. Barrangou, S. Moineau, W.F. Fagan, B. Levin, P.L.F. Johnson. 2018. {\bf Immune Loss as a Driver of Coexistence During Host-Phage Coevolution}. \emph{The ISME Journal} 12(2), 585-597. %(https://doi.org/10.1038/ismej.2017.194)

\end{enumerate} 

 \section{Preprints:} \vspace{0mm}
  
 \begin{enumerate}[leftmargin=*]
 \setlength\itemsep{0.25em}


\item \underline{Weissman$^\star$ J.L.}, E.R.O. Dimbo, A.I. Krinos, C. Neely, Y. Yag\"{ues}, D. Nolin, S. Hou, S. Laperriere, D.A. Caron, B. Tully, H. Alexander, J.A. Fuhrman. {\bf Estimating the maximal growth rates of eukaryotic microbes from cultures and metagenomes via codon usage patterns}. \emph{bioRxiv}

\item Ignacio-Espinoza J.C., S. Laperriere, Y. Yeh, \underline{J.L. Weissman}, S. Hou, M. Long, J.A. Fuhrman. {\bf Ribosome-linked mRNA-rRNA chimeras reveal active novel virus host associations}. \emph{bioRxiv}
 

\end{enumerate} 





\end{resume} 
\end{document} 

