% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.6in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
%\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\setlist{nolistsep}
\setlength{\parskip}{2pt}
\setlength{\parindent}{0pt}
\usepackage{hyperref}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
%\lhead{(ii) CV}
%\rhead{Jake L. Weissman}
\lfoot{CV}
\rfoot{Page \thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\begin{document} 
 \small
\name{Jackie Lee ``JL'' Weissman\\[12pt]} % the \\[12pt] adds a blank line after name
 
 

\address{{\bf pronouns:} they/them/theirs {\emph{or}} she/her/hers\\ {\bf email:} jackie.weissman@stonybrook.edu}
\address{{\bf website:} https://microbialgamut.com/}%{\bf twitter:} @jlw\_ecoevo}

 
\begin{resume} 
 
%\section{Objective} 
%Position as an undergraduate researcher at the Eco-Informatics Summer Institute

 \section{\underline{Positions:}} %\vspace{2mm}
\begin{itemize}[leftmargin=*]
\setlength\itemsep{0.5em}
\item[] {\bf Assistant Professor}, Department of Ecology \& Evolution and the Institute for Advanced Computational Science (IACS), Stony Brook University, Fall 2024 - Present
\item[] {\bf Director of Proposal Development}, City College of New York, New York, NY, 2023 - 2024
\begin{itemize}[leftmargin=*]
\item \emph{Previously: Assistant Director of Proposal Development}
\end{itemize}
%\item[] {\bf Assistant Director of Proposal Development}, CCNY, New York, NY, Summer/Fall 2023
\item[] {\bf Assistant Professor of Computational Biology}, Schmid College of Science and Technology, Chapman University, Orange, CA, Spring 2023 \emph{(tenure track, resigned for family reasons)}
\item[] {\bf Postdoctoral Fellow}, Department of Marine and Environmental Biology, University of Southern California, Los Angeles, CA, 2020 - 2022

\section{\underline{Education}} %\vspace{2mm}

\begin{itemize}[leftmargin=*]
\setlength\itemsep{0.5em}
\item[] {\bf Ph.D., Behavior, Ecology, Evolution, and Systematics} (BEES; Fall 2019),
University of Maryland College Park, College Park, MD

\item[] {\bf Graduate Certificate, Computation and Mathematics for Biological Networks} (COMBINE; Fall 2019),
University of Maryland College Park, College Park, MD

\item[]  {\bf B.A., Mathematics and Biology}  (Spring 2015), Bard College, Annandale-on-Hudson, NY
\end{itemize}

 
 \end{itemize}

 
 \section{\underline{Selected Publications} ($^\star$corresponding)} \vspace{1mm}
 {\bf See my online CV (\url{https://www.microbialgamut.com/CV_JLW.pdf}) for a complete list of publications (30 total), teaching experience, and academic service.}

\begin{enumerate}[leftmargin=*]
 \setlength\itemsep{0.2em}
 
\item Osburn E.D., \underline{J.L. Weissman}, M.S. Strickland, M. Bahram, B.W. Stone, S.G. McBride. 2025. {\bf Relative abundances of bacterial phyla are strong indicators of community-scale microbial growth rates in soil}. \emph{Environmental Microbiome} 20(131)
 
\item Kong S., ... C.K. Lardner, \underline{J.L. Weissman$^\star$}. 2025. {\bf Metagenomes and Metagenome-Assembled Genomes from Tidal Lagoons at a New York City Waterfront Park}. \emph{PeerJ} 13:e20081
 
\item Sinnott-Armstrong N., D. Forsythe, J.M. Benoit, C.R. Chappell, L.S.Y. Coe, B.F.R. de Oliveira, N.C. Evans, A.C. Fagre, J.M. Gilligan, M. Hamilton, C.M. Henneberry, S.L. Ishaq, J. Johnston, E. Krichilsky, J. Alcira Lopez, K. McMonigal, M. Ortiz Alvarez de la Campa, R. Rahman, N.E. Schwartz, L. Talluto, E.J. Taylor, J.M. Vargas-Muñiz, \underline{J.L. Weissman}. 2025. {\bf Protect Transgender Scientists}. \emph{Science}  388(6753), 1283-1284.
 
\item Buchanan P.J., X. Sun, \underline{J.L. Weissman}, D. McCoy, D. Bianchi, E. Zakem. 2025. {\bf Oxygen intrusions sustain aerobic nitrite 
oxidation in anoxic marine zones}. \emph{Science} 388(6751), 1069-1074.
 
 
\item Zakem E.J., J. McNichol$^\dagger$, \underline{J.L. Weissman}$^\dagger$, Y. Raut, L. Xu, E.R. Halewood, C.A. Carlson, S. Dutkiewicz, J.A. Fuhrman, N.M. Levine. 2025. {\bf Functional biogeography of marine microbial heterotrophs}. \emph{Science} 388(6749), eado5323.
 
\item Xu L., E. Zakem, \underline{J.L. Weissman$^\star$}. 2025. {\bf Improved maximum growth rate prediction from microbial genomes by integrating phylogenetic information.} \emph{Nature Communications} 16(1), 1-10.
 
\item \underline{Weissman$^\star$ J.L.}, C.R. Chappell, B.F.R. de Oliveira, N. Evans, A.C. Fagre, D. Forsythe, S.A. Frese, R. Gregor, S.L. Ishaq, J. Johnston, Bittu K.R., S.B. Matsuda, S. McCarren, M.O.A. de la Campa, T.A. Roepke, N. Sinnott-Armstrong, C.S. Stobie, L. Talluto, J. Vargas-Muñiz, The Advancing Queer and Trans Equity in Science (AQTES) Consortium. 2024. {\bf Queer- and trans-inclusive faculty hiring—A call for change}. \emph{PLOS Biology} 22(11), e3002919.

 \item McDonald M.D., C. Owusu-Ansah, J.B. Ellenbogen, Z.D. Malone, M.P. Ricketts, S. Frolking, J.G. Ernakovich, M. Ibba, S.C. Bagby, \underline{J.L. Weissman$^\star$}. 2024. {\bf What is Microbial Dormancy?}. \emph{Trends in Microbiology}

 \item Gregor R., J. Johnston, L. Shu Yang Coe, T. Evans, D. Forsythe, R. Jones, D. Muratore, B.F. Rodrigues de Oliveira, R. Szabo, Y. Wan, J. Williams, Queer and Trans in Microbiology Consortium, \underline{J.L. Weissman$^\star$}. 2023. {\bf Building a Queer- and Trans-Inclusive Microbiology Conference}. \emph{mSystems} 8(5), e00433-23.
 
 
  \item \underline{Weissman$^\star$ J.L.}, M. Peras, T.P. Barnum, J.A. Fuhrman. 2022. {\bf Benchmarking community-wide estimates of growth potential from metagenomes using codon usage statistics}. \emph{mSystems} 7(5), e00745-22.
  
\item \underline{Weissman$^\star$ J.L.}, S. Hou, J.A. Fuhrman. 2021. {\bf Estimating maximal microbial growth rates from cultures, metagenomes, and single cells via codon usage patterns}. \emph{Proceedings of the National Academy of Sciences} 118(12), e2016810118. 
 
\item \underline{Weissman$^\star$ J.L.}, E.O. Alseth, S. Meaden, E.R. Westra, J.A. Fuhrman. 2021. {\bf Immune Lag Is a Major Cost of Prokaryotic Adaptive Immunity During Viral Outbreaks}. \emph{Proceedings of the Royal Society B} 288, 20211555.

\item \underline{Weissman J.L.}, ..., P.L.F. Johnson, D. Karig, W.F. Fagan, S. Bewick. 2021. {\bf Exploring the functional composition of the human microbiome using a hand-curated microbial trait database.} \emph{BMC Bioinformatics} 22(1), 1471-2105.


\item \underline{Weissman J.L.}, A. Stoltzfus, E.R. Westra, P.L.F. Johnson. 2020. {\bf Avoidance of Self During CRISPR Immunization.} \emph{Trends in Microbiology} 28(7), 543-553.

\item \underline{Weissman J.L.} \& P.L.F. Johnson. 2020. {\bf Network-Based Prediction of Novel CRISPR-Associated Genes in Metagenomes.} \emph{mSystems} 5(1), e00752-19.

 \item \underline{Weissman J.L.}, W.F. Fagan, P.L.F. Johnson. 2019. {\bf Linking high GC content to the repair of double strand breaks in prokaryotic genomes.} \emph{PLOS Genetics} 15(11), e1008493. %(https://doi.org/10.1371/journal.pgen.1008493).
 
 \item \underline{Weissman J.L.}, R. Laljani, W.F. Fagan, P.L.F. Johnson. 2019. {\bf Visualization and prediction of CRISPR incidence in microbial trait-space to identify drivers of antiviral immune strategy}. \emph{The ISME Journal} 13(10), 2589-2602. %(https://doi.org/10.1038/s41396-019-0411-2)

 \item \underline{Weissman J.L.}, W.F. Fagan, P.L.F. Johnson. 2018. {\bf Selective maintenance of multiple CRISPR arrays across prokaryotes}. \emph{The CRISPR Journal} 1(6), 405-413. %(https://doi.org/10.1089/crispr.2018.0034) 
 

\item \underline{Weissman J.L.}, R. Holmes, R. Barrangou, S. Moineau, W.F. Fagan, B. Levin, P.L.F. Johnson. 2018. {\bf Immune Loss as a Driver of Coexistence During Host-Phage Coevolution}. \emph{The ISME Journal} 12(2), 585-597. %(https://doi.org/10.1038/ismej.2017.194)

\end{enumerate} 

 \section{Selected Preprints:} \vspace{0mm}
  
 \begin{enumerate}[leftmargin=*]
 \setlength\itemsep{0.25em}

\item \underline{Weissman J.L.$^\star$},  A. Walling, E. Zakem.{\bf  On Copiotrophy and Temperature: Controls on Microbial Maximum Growth Rate Versus Translation Rate Optimization.}  \emph{bioRXiv} 

\item Natarajan J. \& \underline{J.L. Weissman$^\star$}. {\bf Assembly-Free Short-Read Metagenomic Maximum Growth Rate Prediction.} \emph{bioRXiv} 
 
\item \underline{Weissman J.L.$^\star$}, J.M. O'Brien, N.D. Blais, H. Holland-Moritz, K. Shek, R.A. Barbato, T.A. Douglas, J. Gilman Ernakovich. {\bf Growth Optimization Predicts Microbial Success in a Permafrost Thaw Experiment.} \emph{bioRXiv}
 

\end{enumerate} 


  \section{\underline{Selected External Funding}} %\vspace{2mm}
\begin{itemize} 
\item[] {\bf Chemical Currencies of a Microbial Planet (C-CoMP) Faculty Fellow} ($\$40,000$),\\ C-CoMP NSF STC, 2025-2026\\\emph{Inferring Microbial Growth in Communities to Understand a Changing Climate}\\
\item[] {\bf Clean Energy and Technology Careers (Collaborator)} ($\$2,640$ In-Kind to SBU),\\Con Edison (to Genspace as lead), 2026\\\emph{Regenerative Materials, Resilient Careers: Designing Curricula for New York’s Sustainable Workforce}\\
\item[] {\bf Simons Foundation Postdoctoral Fellowship in Marine Microbial Ecology} ($\$246,100$),\\ Simons Foundation, 2020-2023\\\emph{Drafting an Atlas of Prokaryotic Immune Strategy in the Global Oceans}
\end{itemize} 



\end{resume} 
\end{document} 

